### 2022-02-21 paper/output/document/thesis_2_methods.tex
started chapter 5

A maxim itself is an object with a thin representation for a computer, as compared to more complex 
objects like states of affairs or moral character. Later in my project, I argue that a maxim can be 
represented simply as a tuple of circumstances, act, and goal.\footnote{For more, see Section \ref{whatisamaxim}.} 
This representation is simple and efficient, especially when compared to the representations of a causal 
chain or a state of affairs or moral character. This property not only reduces the computational complexity
(in terms of time and space) of representing a maxim, but it also makes the system easier for human reasoners
to interact with. A person crafting an input to a Kantian automated agent needs to reason about relatively
simple units of evaluation, as opposed to the more complex features that consequentialism and virtue
ethics require.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\noindent \textbf{Difficulties in Automation}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
One challenge for automating Kantian ethics is the need for ``common-sense'', or factual and 
situational background. Common-sense is needed when formulating a maxim and when determining if a maxim 
violates the Formula of Universal Law. Maxims include the circumstances in which they apply and
determining which circumstances are ``morally relevant'' to a maxim requires factual background. 
Many misunderstandings in Kantian ethics are due to badly formulated maxims, so this question is 
important for an ethical reasoner to answer.\footnote{For example, critics of Kantian ethics worry 
that the maxim, ``When I am a
man, I will marry a man because I want to spend my life with him'' fails the universalizability
test because if all men only married men, sexual reproduction would stop. This argument implies 
that Kantian ethics is homophobic. Kantians often respond by arguing that the correct formulation of 
this maxim is, ``When I love a man, I will marry him because I want to spend my life with him,'' which
is universalizable because if everyone marries who they love, some men will marry women and others will
marry men.} My system does not need to answer this question because I assume a properly crafted
maxim as input and apply the categorical imperative to this input. Using my system in a fully automated
moral agent will require answering this question, a challenging computational and philosophical task.\footnote{I
discuss this problem in greater detail in Section \ref{whatisamaxim} and Section Limitations.}

@@

%:%443=327%:%
%:%444=328%:%
%:%445=329%:%
%:%446=330%:%
%:%447=331%:%
%:%448=332%:%
%:%449=333%:%
%:%458=335%:%

@@

%:%512=380%:%
%:%513=381%:%
%:%514=382%:%
%:%515=383%:%
%:%516=384%:%
%:%517=385%:%
%:%518=386%:%
%:%527=388%:%
%:%539=390%:%
%:%540=391%:%

@@

%:%565=415%:%
%:%566=416%:%
%:%567=417%:%
%:%568=418%:%
%:%569=419%:%
%:%570=420%:%
%:%571=421%:%

@@

%:%595=443%:%
%:%596=444%:%
%:%597=445%:%
%:%598=446%:%
%:%599=447%:%
%:%600=448%:%
%:%601=449%:%
%:%610=452%:%
%:%622=454%:%
%:%623=455%:%
%:%624=456%:%
%:%625=457%:%
%:%626=458%:%
%:%627=459%:%
%:%636=462%:%
%:%648=464%:%
%:%649=465%:%
%:%650=466%:%
%:%652=468%:%
%:%653=468%:%
%:%654=468%:%
%:%655=468%:%
%:%657=469%:%
%:%658=470%:%
%:%659=470%:%
%:%660=471%:%
%:%661=472%:%
%:%662=472%:%
%:%663=472%:%
%:%664=472%:%
%:%666=473%:%
%:%667=474%:%
%:%668=474%:%
%:%671=488%:%
%:%672=489%:%
%:%673=490%:%
%:%675=492%:%
%:%676=492%:%
%:%677=492%:%
%:%678=492%:%
%:%679=493%:%

@@

%:%681=493%:%
%:%684=497%:%
%:%685=498%:%
%:%686=499%:%
%:%687=500%:%
%:%689=502%:%
%:%690=502%:%
%:%691=526%:%
%:%692=527%:%
%:%694=528%:%
%:%695=529%:%
%:%696=530%:%
%:%697=531%:%
%:%698=531%:%
%:%706=538%:%
%:%718=540%:%
%:%719=541%:%
%:%720=542%:%
%:%721=543%:%
%:%722=544%:%
%:%723=545%:%
%:%724=546%:%
%:%728=562%:%
%:%730=563%:%
%:%731=563%:%
%:%732=564%:%
%:%734=565%:%
%:%735=566%:%
%:%736=566%:%
%:%737=567%:%
%:%738=567%:%
%:%739=568%:%
%:%741=569%:%
%:%744=571%:%
%:%746=572%:%
%:%747=572%:%
%:%748=573%:%
%:%750=574%:%
%:%751=574%:%
%:%754=594%:%
%:%755=595%:%
%:%757=596%:%
%:%758=596%:%
%:%759=597%:%
%:%760=598%:%
%:%761=598%:%
%:%762=599%:%
%:%763=600%:%
%:%764=600%:%
%:%765=601%:%
%:%767=602%:%
%:%768=603%:%
%:%771=605%:%
%:%773=606%:%
%:%774=606%:%
%:%775=607%:%
%:%777=608%:%
%:%778=608%:%
%:%781=616%:%
%:%782=617%:%
%:%783=618%:%
%:%784=619%:%
%:%786=622%:%
%:%787=622%:%
%:%788=622%:%
%:%790=622%:%
%:%794=622%:%
%:%795=622%:%
%:%797=623%:%
%:%798=624%:%
%:%799=624%:%
%:%801=625%:%
%:%802=626%:%
%:%803=627%:%
%:%813=629%:%
%:%814=630%:%
%:%815=631%:%

>>>>

A maxim itself is an object with a thin representation for a computer, as compared to more complex 
objects like states of affairs or moral character. Later in my project, I argue that a maxim can be 
represented simply as a tuple of circumstances, act, and goal.\footnote{For more, see Section \ref{whatisamaxim}.} 
This representation is simple and efficient, especially when compared to the representations of a causal 
chain or a state of affairs or moral character. This property not only reduces the computational complexity
(in terms of time and space) of representing a maxim, but it also makes the system easier for human reasoners
to interact with. A person crafting an input to a Kantian automated agent needs to reason about relatively
simple units of evaluation, as opposed to the more complex features that consequentialism and virtue
ethics require.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\noindent \textbf{Difficulties in Automation}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
One challenge for automating Kantian ethics is the need for ``common-sense'', or factual and 
situational background. Common-sense is needed when formulating a maxim and when determining if a maxim 
violates the Formula of Universal Law. Maxims include the circumstances in which they apply and
determining which circumstances are ``morally relevant'' to a maxim requires factual background. 
Many misunderstandings in Kantian ethics are due to badly formulated maxims, so this question is 
important for an ethical reasoner to answer. My system does not need to answer this question because I assume a properly crafted
maxim as input and apply the categorical imperative to this input. Using my system in a fully automated
moral agent will require answering this question, a challenging computational and philosophical task. I
discuss this problem in greater detail in Section \ref{whatisamaxim} and Section \ref{AIethics}.

@@

%:%451=328%:%
%:%463=331%:%
%:%464=332%:%
%:%465=333%:%
%:%466=334%:%
%:%467=335%:%
%:%468=336%:%
%:%469=337%:%

@@

%:%520=381%:%
%:%532=383%:%
%:%533=384%:%
%:%537=387%:%
%:%538=388%:%
%:%539=389%:%
%:%540=390%:%
%:%541=391%:%
%:%542=392%:%
%:%543=393%:%

@@

%:%568=416%:%
%:%569=417%:%
%:%570=418%:%
%:%571=419%:%
%:%572=420%:%
%:%573=421%:%
%:%574=422%:%

@@

%:%603=445%:%
%:%615=447%:%
%:%616=448%:%
%:%617=449%:%
%:%618=450%:%
%:%619=451%:%
%:%620=452%:%
%:%629=455%:%
%:%641=457%:%
%:%642=458%:%
%:%643=459%:%
%:%645=461%:%
%:%646=461%:%
%:%647=461%:%
%:%648=461%:%
%:%650=462%:%
%:%651=463%:%
%:%652=463%:%
%:%653=464%:%
%:%654=465%:%
%:%655=465%:%
%:%656=465%:%
%:%657=465%:%
%:%659=466%:%
%:%660=467%:%
%:%661=467%:%
%:%664=481%:%
%:%665=482%:%
%:%666=483%:%
%:%668=485%:%
%:%669=485%:%
%:%670=485%:%
%:%671=485%:%
%:%672=486%:%
%:%673=486%:%
%:%674=486%:%
%:%677=490%:%
%:%678=491%:%
%:%679=492%:%

@@

%:%682=495%:%
%:%683=495%:%
%:%684=519%:%
%:%685=520%:%
%:%687=521%:%
%:%688=522%:%
%:%689=523%:%
%:%690=524%:%
%:%691=524%:%
%:%699=531%:%
%:%711=533%:%
%:%712=534%:%
%:%713=535%:%
%:%714=536%:%
%:%715=537%:%
%:%716=538%:%
%:%717=539%:%
%:%721=555%:%
%:%723=556%:%
%:%724=556%:%
%:%725=557%:%
%:%727=558%:%
%:%728=559%:%
%:%729=559%:%
%:%730=560%:%
%:%731=560%:%
%:%732=561%:%
%:%734=562%:%
%:%737=564%:%
%:%739=565%:%
%:%740=565%:%
%:%741=566%:%
%:%743=567%:%
%:%744=567%:%
%:%747=587%:%
%:%748=588%:%
%:%750=589%:%
%:%751=589%:%
%:%752=590%:%
%:%753=591%:%
%:%754=591%:%
%:%755=592%:%
%:%756=593%:%
%:%757=593%:%
%:%758=594%:%
%:%760=595%:%
%:%761=596%:%
%:%764=598%:%
%:%766=599%:%
%:%767=599%:%
%:%768=600%:%
%:%770=601%:%
%:%771=601%:%
%:%774=609%:%
%:%775=610%:%
%:%776=611%:%
%:%777=612%:%
%:%779=615%:%
%:%780=615%:%
%:%781=615%:%
%:%783=615%:%
%:%787=615%:%
%:%788=615%:%
%:%790=616%:%
%:%791=617%:%
%:%792=617%:%
%:%794=618%:%
%:%795=619%:%
%:%796=620%:%
%:%806=622%:%
%:%807=623%:%
%:%808=624%:%

### 2022-02-21 paper/output/document/thesis_3_implementation.tex
started chapter 5

O'Neill seems to acknowledge the difficulty of determining relevant circumstances when she concedes that a maxim cannot include all 
of the infinitely many circumstances in which the agent may perform an action \citep[4:428]{actingonprinciple}. She argues that this is 
an artifact of the fact that maxims are rules of practical reason, the kind of reason that helps us decide what to do 
and how to do it \citep{bok}. Like any practical rule, 
maxims require the exercise of practical judgement to determine in which circumstances they should be applied. 
This judgement, applied in both choosing when to exercise the maxim and in the formulation of the maxim 
itself, is what determines the morally relevant circumstances.

The difficulty in determining relevant circumstances is a limitation of my system and requires that a 
human being formulate the maxim or that future work develop heuristics to classify circumstances as morally 
relevant. For proponents of the ``human-in-the-loop'' model of AI ethics, in which ethical AI requires that 
humans guide machines, human involvement may be a feature, not a bug \citep{loop}. In this model, 
a human being must create a representation for the dilemma they wish to test, translating 
a complex situation into a flat logical structure. This parallels the challenge that programmers 
face when translating the complexity of reality to a programming langauge or computational representation. 
The outcome of the universalizability test will depend on how the human formulates the maxim; if the 
human puts garbage into the test, the test will return garbage out.

Another solution is to develop heuristics to classify circumstances as morally 
relevant. For example, one such attempt could define a moral closeness relation between an action, a 
goal, and circumstances. This heuristic could define morally relevant circumstances as those that 
reach a certain closeness threshhold with the action and the goal. Another possible heuristic could 
define some set of morally important entities, and classify morally relevant circumstances as those
that involve morally important entities. Determining morally relevant
circumstances, either using heuristics or human involvement, is a ripe area for future work.

@@

\isamarkupsubsubsection{Formalizing the FUL%

@@

%:%231=146%:%

@@

%:%233=148%:%
%:%234=149%:%
%:%235=150%:%
%:%236=151%:%
%:%237=152%:%
%:%238=153%:%
%:%239=154%:%
%:%240=155%:%
%:%241=156%:%
%:%242=157%:%
%:%243=158%:%
%:%244=159%:%
%:%245=160%:%
%:%247=162%:%
%:%248=162%:%
%:%249=163%:%
%:%251=164%:%
%:%252=165%:%
%:%253=166%:%
%:%254=167%:%
%:%262=169%:%

@@

%:%310=207%:%
%:%311=208%:%

@@

%:%314=211%:%
%:%315=212%:%
%:%316=213%:%
%:%317=214%:%
%:%318=215%:%
%:%319=216%:%
%:%320=217%:%
%:%321=218%:%
%:%322=219%:%
%:%323=220%:%
%:%324=221%:%
%:%326=224%:%
%:%327=224%:%
%:%328=225%:%
%:%330=226%:%
%:%331=227%:%

@@

%:%341=236%:%
%:%342=237%:%

@@

%:%345=240%:%
%:%346=241%:%
%:%347=242%:%
%:%348=243%:%
%:%349=244%:%
%:%350=245%:%
%:%351=246%:%
%:%352=247%:%
%:%353=248%:%
%:%354=249%:%
%:%355=250%:%

@@

%:%358=253%:%
%:%359=254%:%
%:%361=255%:%
%:%362=256%:%
%:%363=256%:%
%:%366=262%:%
%:%367=263%:%
%:%368=264%:%
%:%369=265%:%
%:%370=266%:%
%:%371=267%:%
%:%372=268%:%
%:%373=269%:%
%:%374=270%:%
%:%375=271%:%
%:%376=272%:%
%:%378=274%:%
%:%379=274%:%
%:%380=275%:%
%:%382=276%:%

@@

%:%403=296%:%

@@

%:%405=298%:%
%:%406=299%:%
%:%407=300%:%
%:%408=301%:%
%:%409=302%:%
%:%410=303%:%
%:%411=304%:%
%:%412=305%:%
%:%413=306%:%
%:%414=307%:%
%:%415=308%:%
%:%416=309%:%
%:%417=310%:%
%:%419=312%:%
%:%420=312%:%
%:%421=313%:%
%:%423=314%:%
%:%424=315%:%
%:%425=315%:%
%:%426=316%:%
%:%427=317%:%
%:%428=317%:%
%:%429=318%:%
%:%431=319%:%
%:%432=320%:%
%:%435=322%:%
%:%436=323%:%
%:%437=324%:%
%:%438=325%:%
%:%440=327%:%
%:%441=327%:%
%:%442=328%:%
%:%444=329%:%
%:%445=330%:%
%:%446=330%:%
%:%447=331%:%
%:%448=332%:%
%:%449=332%:%
%:%451=333%:%
%:%452=334%:%
%:%453=335%:%
%:%461=337%:%
%:%473=339%:%
%:%474=340%:%
%:%475=341%:%
%:%476=342%:%
%:%477=343%:%
%:%478=344%:%
%:%479=345%:%
%:%480=346%:%
%:%482=349%:%
%:%483=349%:%
%:%485=350%:%
%:%486=351%:%
%:%487=352%:%
%:%488=353%:%
%:%491=355%:%
%:%492=356%:%
%:%494=358%:%
%:%495=358%:%
%:%497=358%:%
%:%501=358%:%
%:%502=358%:%
%:%503=359%:%
%:%504=359%:%
%:%505=359%:%

@@

%:%524=371%:%

@@

%:%526=373%:%
%:%527=374%:%
%:%528=375%:%
%:%529=376%:%
%:%530=377%:%
%:%531=378%:%
%:%532=379%:%
%:%533=380%:%
%:%534=381%:%
%:%535=382%:%
%:%536=383%:%
%:%537=384%:%
%:%538=385%:%
%:%540=387%:%
%:%541=387%:%
%:%542=388%:%
%:%544=389%:%
%:%545=390%:%
%:%548=392%:%
%:%550=394%:%
%:%551=394%:%
%:%552=395%:%
%:%554=396%:%
%:%555=397%:%
%:%556=397%:%
%:%557=398%:%
%:%558=399%:%
%:%559=399%:%
%:%560=400%:%
%:%561=400%:%
%:%563=400%:%
%:%567=400%:%
%:%568=400%:%
%:%570=401%:%
%:%571=402%:%
%:%572=403%:%
%:%573=404%:%
%:%574=405%:%
%:%575=406%:%
%:%576=407%:%

@@

%:%592=415%:%

@@

%:%594=417%:%
%:%595=418%:%
%:%596=419%:%
%:%597=420%:%
%:%598=421%:%
%:%599=422%:%
%:%600=423%:%
%:%601=424%:%
%:%602=425%:%
%:%603=426%:%
%:%604=427%:%
%:%605=428%:%
%:%606=429%:%
%:%608=431%:%
%:%609=431%:%
%:%611=433%:%
%:%612=434%:%
%:%613=435%:%
%:%614=436%:%
%:%615=437%:%
%:%624=439%:%

@@

%:%646=451%:%
%:%647=452%:%
%:%648=453%:%
%:%649=454%:%
%:%650=455%:%
%:%651=456%:%
%:%652=457%:%
%:%653=458%:%
%:%654=459%:%
%:%655=460%:%

@@

%:%663=469%:%
%:%664=470%:%
%:%665=471%:%
%:%666=472%:%
%:%667=473%:%
%:%668=474%:%
%:%671=476%:%
%:%672=477%:%
%:%673=478%:%
%:%674=479%:%
%:%675=480%:%
%:%676=481%:%
%:%677=482%:%
%:%678=483%:%
%:%679=484%:%
%:%680=485%:%

@@

%:%685=488%:%
%:%686=489%:%
%:%687=490%:%
%:%688=491%:%
%:%689=492%:%
%:%690=493%:%
%:%691=494%:%
%:%692=495%:%
%:%693=496%:%
%:%694=497%:%
%:%695=498%:%
%:%696=499%:%
%:%697=500%:%
%:%699=502%:%
%:%700=502%:%
%:%701=503%:%
%:%704=504%:%
%:%708=504%:%
%:%709=504%:%
%:%711=505%:%
%:%712=506%:%
%:%713=507%:%
%:%714=507%:%
%:%716=508%:%
%:%717=509%:%
%:%718=510%:%
%:%719=511%:%
%:%725=511%:%
%:%728=512%:%
%:%729=513%:%
%:%730=513%:%
%:%731=514%:%
%:%734=515%:%
%:%738=515%:%
%:%739=515%:%
%:%741=516%:%
%:%742=517%:%

@@

%:%758=525%:%

@@

%:%760=527%:%
%:%761=528%:%
%:%762=529%:%
%:%763=530%:%
%:%764=531%:%
%:%765=532%:%
%:%766=533%:%
%:%767=534%:%
%:%768=535%:%
%:%769=536%:%
%:%770=537%:%
%:%771=538%:%
%:%772=539%:%
%:%774=541%:%
%:%775=541%:%
%:%776=542%:%
%:%779=543%:%
%:%783=543%:%
%:%784=543%:%
%:%785=543%:%
%:%787=544%:%
%:%793=544%:%
%:%796=545%:%
%:%797=546%:%
%:%798=546%:%
%:%799=547%:%
%:%800=548%:%
%:%803=549%:%
%:%807=549%:%
%:%808=549%:%
%:%809=549%:%
%:%811=550%:%
%:%812=551%:%
%:%813=552%:%
%:%823=554%:%
%:%824=555%:%
%:%825=556%:%
%:%826=557%:%
%:%827=558%:%
%:%828=559%:%
%:%829=560%:%
%:%830=561%:%
%:%832=564%:%
%:%833=564%:%
%:%836=565%:%
%:%840=565%:%
%:%841=565%:%
%:%843=566%:%
%:%844=567%:%
%:%845=568%:%
%:%855=570%:%
%:%856=571%:%
%:%857=572%:%
%:%858=573%:%
%:%859=574%:%
%:%860=575%:%
%:%861=576%:%
%:%863=578%:%
%:%864=578%:%
%:%865=579%:%
%:%866=580%:%
%:%869=581%:%
%:%873=581%:%
%:%874=581%:%
%:%875=581%:%
%:%877=582%:%
%:%878=583%:%
%:%879=584%:%
%:%889=586%:%
%:%890=587%:%
%:%892=589%:%
%:%893=589%:%
%:%894=590%:%
%:%895=591%:%
%:%898=592%:%
%:%902=592%:%
%:%903=592%:%
%:%904=592%:%
%:%906=593%:%
%:%916=595%:%
%:%917=596%:%

@@

%:%926=605%:%
%:%927=606%:%
%:%928=607%:%
%:%929=608%:%
%:%933=612%:%
%:%934=613%:%
%:%935=614%:%
%:%936=615%:%
%:%937=616%:%
%:%938=617%:%
%:%939=618%:%
%:%940=619%:%

@@

%:%948=626%:%
%:%949=627%:%
%:%950=628%:%
%:%951=629%:%
%:%952=630%:%
%:%953=631%:%
%:%954=632%:%
%:%955=633%:%
%:%956=634%:%
%:%957=635%:%
%:%958=636%:%
%:%959=637%:%
%:%960=638%:%
%:%961=639%:%
%:%962=640%:%

>>>>

O'Neill seems to acknowledge the difficulty of determining relevant circumstances when she concedes that a maxim cannot include all 
of the infinitely many circumstances in which the agent may perform an action \citep[4:428]{actingonprinciple}. She argues that this is 
an artifact of the fact that maxims are rules of practical reason, the kind of reason that helps us decide what to do 
and how to do it \citep{bok}. Like any practical rule, 
maxims require the exercise of practical judgement to determine in which circumstances they should be applied. 
This judgement, applied in both choosing when to exercise the maxim and in the formulation of the maxim 
itself, is what determines the morally relevant circumstances.  
The difficulty in determining relevant circumstances is a limitation of my system and requires that a 
human being formulate the maxim or that future work develop heuristics to classify circumstances as morally 
relevant. I discuss this challenge and potential solutions in greater detail in Section \ref{commonsense}.

@@

\isamarkupsubsubsection{Formalizing the FUL\label{formalizingful}%

@@

@@

%:%233=147%:%
%:%234=148%:%
%:%236=149%:%
%:%237=150%:%
%:%238=151%:%
%:%239=152%:%
%:%247=154%:%
%:%259=156%:%
%:%260=157%:%
%:%261=158%:%
%:%262=159%:%
%:%263=160%:%
%:%264=161%:%
%:%265=162%:%
%:%266=163%:%
%:%267=164%:%
%:%268=165%:%
%:%269=166%:%
%:%270=167%:%
%:%271=168%:%
%:%272=169%:%
%:%273=170%:%

@@

%:%311=209%:%

@@

%:%315=211%:%
%:%316=212%:%
%:%319=214%:%
%:%320=215%:%
%:%321=216%:%
%:%322=217%:%
%:%323=218%:%
%:%324=219%:%
%:%325=220%:%
%:%326=221%:%
%:%327=222%:%
%:%328=223%:%
%:%329=224%:%
%:%330=225%:%
%:%331=226%:%
%:%332=227%:%
%:%333=228%:%

@@

%:%342=238%:%

@@

%:%346=240%:%
%:%347=241%:%
%:%348=241%:%
%:%351=247%:%
%:%352=248%:%
%:%353=249%:%
%:%354=250%:%
%:%355=251%:%
%:%356=252%:%

@@

%:%358=254%:%
%:%359=255%:%
%:%360=256%:%
%:%361=257%:%
%:%363=259%:%
%:%364=259%:%
%:%365=260%:%
%:%367=261%:%
%:%370=263%:%
%:%371=264%:%
%:%372=265%:%
%:%373=266%:%
%:%374=267%:%
%:%375=268%:%
%:%376=269%:%
%:%377=270%:%
%:%378=271%:%
%:%379=272%:%
%:%380=273%:%
%:%381=274%:%
%:%382=275%:%
%:%383=276%:%
%:%384=277%:%

@@

@@

%:%405=297%:%
%:%406=298%:%
%:%408=299%:%
%:%409=300%:%
%:%410=300%:%
%:%411=301%:%
%:%412=302%:%
%:%413=302%:%
%:%414=303%:%
%:%416=304%:%
%:%417=305%:%
%:%420=307%:%
%:%421=308%:%
%:%422=309%:%
%:%423=310%:%
%:%425=312%:%
%:%426=312%:%
%:%427=313%:%
%:%429=314%:%
%:%430=315%:%
%:%431=315%:%
%:%432=316%:%
%:%433=317%:%
%:%434=317%:%
%:%436=318%:%
%:%437=319%:%
%:%438=320%:%
%:%446=322%:%
%:%458=324%:%
%:%459=325%:%
%:%460=326%:%
%:%461=327%:%
%:%462=328%:%
%:%463=329%:%
%:%464=330%:%
%:%465=331%:%
%:%467=334%:%
%:%468=334%:%
%:%470=335%:%
%:%471=336%:%
%:%472=337%:%
%:%473=338%:%
%:%476=340%:%
%:%477=341%:%
%:%479=343%:%
%:%480=343%:%
%:%482=343%:%
%:%486=343%:%
%:%487=343%:%
%:%488=344%:%
%:%489=344%:%
%:%490=344%:%
%:%499=346%:%
%:%500=347%:%
%:%501=348%:%
%:%502=349%:%
%:%503=350%:%
%:%504=351%:%
%:%505=352%:%
%:%506=353%:%
%:%507=354%:%
%:%508=355%:%
%:%509=356%:%
%:%510=357%:%
%:%511=358%:%
%:%512=359%:%
%:%513=360%:%

@@

@@

%:%526=372%:%
%:%527=373%:%
%:%529=374%:%
%:%530=375%:%
%:%533=377%:%
%:%535=379%:%
%:%536=379%:%
%:%537=380%:%
%:%539=381%:%
%:%540=382%:%
%:%541=382%:%
%:%542=383%:%
%:%543=384%:%
%:%544=384%:%
%:%545=385%:%
%:%546=385%:%
%:%548=385%:%
%:%552=385%:%
%:%553=385%:%
%:%555=386%:%
%:%556=387%:%
%:%557=388%:%
%:%558=389%:%
%:%559=390%:%
%:%560=391%:%
%:%561=392%:%
%:%571=394%:%
%:%572=395%:%
%:%573=396%:%
%:%574=397%:%
%:%575=398%:%
%:%576=399%:%
%:%577=400%:%
%:%578=401%:%
%:%579=402%:%
%:%580=403%:%
%:%581=404%:%
%:%582=405%:%
%:%583=406%:%
%:%584=407%:%
%:%585=408%:%

@@

@@

%:%594=416%:%
%:%596=418%:%
%:%597=419%:%
%:%598=420%:%
%:%599=421%:%
%:%600=422%:%
%:%609=424%:%
%:%621=426%:%
%:%622=427%:%
%:%623=428%:%
%:%624=429%:%
%:%625=430%:%
%:%626=431%:%
%:%627=432%:%
%:%628=433%:%
%:%629=434%:%
%:%630=435%:%
%:%631=436%:%
%:%632=437%:%
%:%633=438%:%
%:%634=439%:%
%:%635=440%:%

@@

%:%648=454%:%
%:%649=455%:%
%:%650=456%:%
%:%651=457%:%
%:%652=458%:%
%:%653=459%:%

@@

%:%661=466%:%
%:%662=467%:%
%:%663=468%:%
%:%664=469%:%
%:%665=470%:%
%:%669=472%:%
%:%670=473%:%
%:%671=474%:%
%:%672=475%:%
%:%673=476%:%
%:%674=477%:%
%:%675=478%:%
%:%676=479%:%
%:%677=480%:%
%:%678=481%:%
%:%679=482%:%
%:%680=483%:%
%:%681=484%:%
%:%682=485%:%

@@

%:%685=487%:%
%:%686=488%:%
%:%689=489%:%
%:%693=489%:%
%:%694=489%:%
%:%696=490%:%
%:%697=491%:%
%:%698=492%:%
%:%699=492%:%
%:%701=493%:%
%:%702=494%:%
%:%703=495%:%
%:%704=496%:%
%:%710=496%:%
%:%713=497%:%
%:%714=498%:%
%:%715=498%:%
%:%716=499%:%
%:%719=500%:%
%:%723=500%:%
%:%724=500%:%
%:%726=501%:%
%:%727=502%:%
%:%737=504%:%
%:%738=505%:%
%:%739=506%:%
%:%740=507%:%
%:%741=508%:%
%:%742=509%:%
%:%743=510%:%
%:%744=511%:%
%:%745=512%:%
%:%746=513%:%
%:%747=514%:%
%:%748=515%:%
%:%749=516%:%
%:%750=517%:%
%:%751=518%:%

@@

@@

%:%760=526%:%
%:%761=527%:%
%:%764=528%:%
%:%768=528%:%
%:%769=528%:%
%:%770=528%:%
%:%772=529%:%
%:%778=529%:%
%:%781=530%:%
%:%782=531%:%
%:%783=531%:%
%:%784=532%:%
%:%785=533%:%
%:%788=534%:%
%:%792=534%:%
%:%793=534%:%
%:%794=534%:%
%:%796=535%:%
%:%797=536%:%
%:%798=537%:%
%:%808=539%:%
%:%809=540%:%
%:%810=541%:%
%:%811=542%:%
%:%812=543%:%
%:%813=544%:%
%:%814=545%:%
%:%815=546%:%
%:%817=549%:%
%:%818=549%:%
%:%821=550%:%
%:%825=550%:%
%:%826=550%:%
%:%828=551%:%
%:%829=552%:%
%:%830=553%:%
%:%840=555%:%
%:%841=556%:%
%:%842=557%:%
%:%843=558%:%
%:%844=559%:%
%:%845=560%:%
%:%846=561%:%
%:%848=563%:%
%:%849=563%:%
%:%850=564%:%
%:%851=565%:%
%:%854=566%:%
%:%858=566%:%
%:%859=566%:%
%:%860=566%:%
%:%862=567%:%
%:%863=568%:%
%:%864=569%:%
%:%874=571%:%
%:%875=572%:%
%:%877=574%:%
%:%878=574%:%
%:%879=575%:%
%:%880=576%:%
%:%883=577%:%
%:%887=577%:%
%:%888=577%:%
%:%889=577%:%
%:%891=578%:%
%:%901=580%:%
%:%902=581%:%
%:%903=582%:%
%:%904=583%:%
%:%905=584%:%
%:%906=585%:%
%:%907=586%:%
%:%908=587%:%
%:%909=588%:%
%:%910=589%:%
%:%911=590%:%
%:%912=591%:%
%:%913=592%:%
%:%914=593%:%

@@

%:%929=607%:%
%:%930=608%:%
%:%931=609%:%
%:%932=610%:%
%:%933=611%:%
%:%934=612%:%
%:%935=613%:%
%:%936=614%:%
%:%937=615%:%
%:%938=616%:%
%:%939=617%:%
%:%940=618%:%
%:%941=619%:%
%:%942=620%:%
%:%943=621%:%

@@
